---
title: "ENDES_TBM_2019"
author: "Carlos Ballon-Salcedo"
format: html
editor: visual
execute:
  echo: false
  warning: false
  message: false
  error: false
  include: true
  results: hide
  cache: false
  fig_caption: true
  fig_width: 6
  fig_height: 4
  out.width: "100%"
  out.extra: |
    class="img-responsive"
    style="display:block; margin-left:auto; margin-right:auto;"
---

# Load packages

```{r}
pacman::p_load(
  rio,
  here,
  tidyverse,
  survey,
  gtsummary,
  finalfit,
  flextable,
  bstfun,
  haven, 
  janitor,
  labelled,
  naniar,
  rfextras)

#source(here::here("scripts", "dictionary.R"))
rfextras::load_scripts()
```

# Import data

```{r}
# 
individual_data <- rio::import(here::here("data", "raw", "RECH1_2023.dta"))

home_data <- rio::import(here::here("data", "raw", "RECH0_2023.dta"))

dwelling_data <- rio::import(here::here("data", "raw", "RECH23_2023.dta"))
```

```{r}
woman_data_1 <- rio::import(here::here("data", "raw", "RECH5_2023.dta"))

woman_data_2 <- rio::import(here::here("data", "raw", "REC0111_2023.dta"))

woman_data_3 <- rio::import(here::here("data", "raw", "REC41_2023.dta"))

woman_data_4 <- rio::import(here::here("data", "raw", "REC42_2023.dta"))

woman_data_5 <- rio::import(here::here("data", "raw", "RE223132_2023.dta"))
```

```{r}
children_data_1 <- rio::import(here::here("data", "raw", "RECH6_2023.dta"))

children_data_2 <- rio::import(here::here("data", "raw", "REC44_2023.dta"))
```

```{r}
health_data <- rio::import(here::here("data", "raw", "CSALUD01_2023.dta"))
```

# Process data

## Normalization of identifiers

```{r}
# Individual data
individual_data <- individual_data |> 
  dplyr::mutate(QSNUMERO = HVIDX)

# Woman data
woman_data_1 <- woman_data_1 |> 
  dplyr::mutate(QSNUMERO = HA0)

woman_data_2 <- woman_data_2 |>
  dplyr::mutate(
    QSNUMERO = str_sub(CASEID, -2, -1),
    QSNUMERO = as.numeric(QSNUMERO))

woman_data_3 <- woman_data_3 |>
  dplyr::mutate(
    HHID = str_sub(CASEID, 1, str_length(CASEID) - 3),
    QSNUMERO = str_sub(CASEID, -2, -1),
    QSNUMERO = as.numeric(QSNUMERO)
  )

woman_data_4 <- woman_data_4 |>
  dplyr::mutate(
    HHID = str_sub(CASEID, 1, str_length(CASEID) - 3),
    QSNUMERO = str_sub(CASEID, -2, -1),
    QSNUMERO = as.numeric(QSNUMERO)
  )

woman_data_5 <- woman_data_5 |>
  dplyr::mutate(
    HHID = str_sub(CASEID, 1, str_length(CASEID) - 3),
    QSNUMERO = str_sub(CASEID, -2, -1),
    QSNUMERO = as.numeric(QSNUMERO)
  )

# Children data
children_data_1 <- children_data_1 |>
  dplyr::mutate(
    HW1 = HC1,
    HW2 = HC2,
    HW3 = HC3,
    HW53 = HC53,
    QSNUMERO = HC60
  ) |>
  dplyr::filter(HC13 == 0) # Filtramos a los ni침os medidos

children_data_2 <- children_data_2 |>
  dplyr::mutate(
    HHID = str_sub(CASEID, 1, str_length(CASEID) - 3),
    QSNUMERO = str_sub(CASEID, -2, -1),
    QSNUMERO = as.numeric(QSNUMERO)
  ) |>
    dplyr::filter(HW13 == 0) # Filtramos a los ni침os medidos
```

```{r}
summary(children_data_1$HC2)
summary(children_data_2$HW2)
```

## Join dataframes

```{r}
# Join mother data
woman_data <- woman_data_1 |>
  dplyr::left_join(woman_data_2, by = c("HHID", "QSNUMERO")) |>
  dplyr::left_join(woman_data_4, by = c("HHID", "QSNUMERO")) |>
  dplyr::left_join(woman_data_5, by = c("HHID", "QSNUMERO"))

# Join children data
children_data <- children_data_1 |>
  dplyr::left_join(children_data_2, by = c("HHID", "QSNUMERO", "HW1", "HW2", "HW3")) |>
  dplyr::rename(MIDX = HWIDX)

# Join children data with mother data
children_mother_data <- children_data |>
  dplyr::left_join(woman_data_3, by = c("HHID", "QSNUMERO", "MIDX"))

# Join home data with dwelling data
home_dwelling_data <- home_data |>
  dplyr::left_join(dwelling_data, by = "HHID")

# Join children/mother data with individual data
children_mother_individual_data <- children_mother_data |>
  dplyr::left_join(individual_data, by = c("HHID","QSNUMERO"))

# Join home/dwelling/individual data with mother data
pre_data <- children_mother_individual_data |>
  dplyr::left_join(woman_data, by = c("HHID","QSNUMERO"))

# Join home/dwelling/individual/mother data with health data
pre_data_1 <- pre_data |> 
  dplyr::left_join(health_data, by = c("HHID","QSNUMERO"))

# Join all
endestc <- pre_data_1 |>
  dplyr::left_join(home_dwelling_data, by = 'HHID')

# Clean names
# endestc <- janitor::clean_names(endestc)

# haven::write_dta(endestc, here::here("data", "endestc.dta"))
```

## Variable selection

```{r}
endes_dbm_tbm <- variable_selection_endes(endestc) |>
  dplyr::filter(currently_pregnant != 1 | is.na(currently_pregnant))
```

## Non-plausible values

```{r}
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    sd_height_age_child = case_when(
      sd_height_age_child > 500  ~ NA_real_,
      sd_height_age_child < -500 ~ NA_real_,
      sd_height_age_child >= 9996 ~ NA_real_,
      TRUE ~ sd_height_age_child
    ),
    sd_weight_height_child = case_when(
      sd_weight_height_child > 500  ~ NA_real_,
      sd_weight_height_child < -500 ~ NA_real_,
      sd_weight_height_child >= 9996 ~ NA_real_,
      TRUE ~ sd_weight_height_child
    ),
    sd_weight_age_child = case_when(
      sd_weight_age_child > 500  ~ NA_real_,
      sd_weight_age_child < -500 ~ NA_real_,
      sd_weight_age_child >= 9996 ~ NA_real_,
      TRUE ~ sd_weight_age_child
    ),
    bmi_mother_1 = (weight_mother / 10) / ((height_mother / 10)^2) * 10000,
    bmi_mother_1 = case_when(
      bmi_mother_1 > 60  ~ NA_real_,
      bmi_mother_1 < 16 ~ NA_real_,
      TRUE ~ bmi_mother_1
    )
  ) |>
  dplyr::filter(
    !is.na(sd_height_age_child),
    !is.na(sd_weight_height_child),
    !is.na(sd_weight_age_child),
    !is.na(bmi_mother_1),
    !is.na(hb_child)
  )
```


```{r}
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::group_by(id) |>
  dplyr::slice_min(age_child, with_ties = TRUE) |>
  dplyr::ungroup()
```


```{r}
#| eval: false
#| include: false
summary(endes_dbm_tbm$age_mother)
summary(endes_dbm_tbm$bmi_mother)
sum(is.na(endes_dbm_tbm$sd_height_age_child))
sum(is.na(endes_dbm_tbm$sd_weight_age_child))
lapply(endes_dbm_tbm, function(x) sum(is.na(x)))

```

## Remove missing values

```{r}

```

## Recode and relevel (dictionary)

reducir tama침o de poblaci칩n, filtrar lima, region, area o los manejamos como confusores

modelo truncado por 0 (solo positivos)
propensity score

```{r}
#RETRAZO EN EL CRECIMIENTO
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    stunting =
      case_when(
        sd_height_age_child < -200  ~ 1,
        sd_height_age_child >= -200 ~ 0,
        sd_height_age_child >= 9996 ~ 99
      )
  ) |>
  naniar::replace_with_na(replace = list(stunting = c(99))) |>
  labelled::set_value_labels(stunting = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(stunting = "Stunted child under 5 years")

table(endes_dbm_tbm$stunting)
str(endes_dbm_tbm$stunting)

endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    wasting =
      case_when(
        sd_weight_height_child < -200  ~ 1,
        sd_weight_height_child >= -200 ~ 0,
        sd_weight_height_child >= 9996 ~ 99
      )
  ) |>
  naniar::replace_with_na(replace = list(wasting = c(99))) |>
  labelled::set_value_labels(wasting = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(wasting = "Wasted child under 5 years")

#Bajo peso
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    underweight =
      case_when(
        sd_weight_age_child < -200  ~ 1,
        sd_weight_age_child >= -200 ~ 0,
        sd_weight_age_child >= 9996 ~ 99
      )
  ) |>
  naniar::replace_with_na(replace = list(underweight = c(99))) |>
  labelled::set_value_labels(underweight = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(underweight = "Underweight child under 5 years")

#Sobrepeso y obesidad
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight =
      case_when(
        sd_weight_age_child > 200  ~ 1,
        sd_weight_age_child <= 200 ~ 0,
        sd_weight_age_child >= 9996 ~ 99
      )
  ) |>
  naniar::replace_with_na(replace = list(overweight = c(99))) |>
  labelled::set_value_labels(overweight = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight = "Overweight child under 5 years")

#Anemia corregida OMS
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    anemia_oms =
      case_when(
        hb_altura_child < 110  ~ 1,
        hb_altura_child >= 110 ~ 0 
      )
  ) |>
  labelled::set_value_labels(anemia_oms = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(anemia_oms = "Anemia child under 5 years")

table(endes_dbm_tbm$anemia_oms)

#MADRE CON SOBREPESO U OBESIDAD
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight_mother =
      case_when(
        bmi_mother_1 > 25  ~ 1,
        bmi_mother_1 <= 25 ~ 0,
      )
  ) |>
  labelled::set_value_labels(overweight_mother = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight_mother = "Mother overweight/obese")

# Undernutrition
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    undernutrition = case_when(
      stunting == 1 | wasting == 1 | underweight == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(undernutrition = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(undernutrition = "Undernutrition")

# Overweight/stunting
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight_stunting = case_when(
      overweight_mother == 1 & stunting == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(overweight_stunting = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight_stunting = "Overweight/stunting")

# Overweight/wasting
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight_wasting = case_when(
      overweight_mother == 1 & wasting == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(overweight_wasting = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight_wasting = "Overweight/wasting")

# Overweight/underweight
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight_underweight = case_when(
      overweight_mother == 1 & underweight == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(overweight_underweight = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight_underweight = "Overweight/underweight")

# Double burden
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    double_burden = case_when(
      overweight_mother == 1 & undernutrition == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(double_burden = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(double_burden = "DBM")

# Overweight/anemia
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    overweight_anemia_oms = case_when(
      overweight_mother == 1 & anemia_oms == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(overweight_anemia_oms = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(overweight_anemia_oms = "Overweight/undernutrition")

# Triple burden
endes_dbm_tbm <- endes_dbm_tbm |>
  dplyr::mutate(
    triple_burden = case_when(
      overweight_mother == 1 & undernutrition == 1 & anemia_oms == 1 ~ 1,
      TRUE ~ 0)
  ) |>
  labelled::set_value_labels(triple_burden = c("Yes" = 1, "No" = 0)) |>
  labelled::set_variable_labels(triple_burden = "TBM")

haven::write_dta(endes_dbm_tbm, here::here("data", "clean", "endes_dbm_tbm.dta"))
```


## Exploratory Data Analysis (EDA)

```{r}
# Filtrada
dbm <- ninios |>
  dplyr::select(hc8, hc57, hc71, hc70, id1, hc72, peso, id1) |>
  na.omit() |>
  dplyr::filter(hc71 < 2000, hc70 < 2000, hc72 < 2000) |>
  dplyr::mutate(hc57 = as.factor(hc57), peso_edad = hc71 / 100, talla_edad = hc70 / 100, peso_talla = hc72 /100) |>
  dplyr::mutate(
    anemia = case_when(hc57 == 4 ~ "Sin Anemia", TRUE ~ "Anemia"),
    talla_edad_dico = case_when(talla_edad < -2 ~ "DCI", TRUE ~ "Normal"),
    peso_edad_dico = case_when(peso_edad > 2 ~ "Exceso de peso", TRUE ~ "Normal"),
    peso_talla_dico = case_when(peso_talla < -2 ~ "Emaciacion", TRUE ~ "Sin emaciacion"),
    peso_talla_dico_1 = case_when(peso_talla > 2 ~ "Exceso de peso", TRUE ~ "Normal"),
    
    DBM_1 = case_when(anemia == "Anemia" & talla_edad_dico == "DCI" ~ "DBM", TRUE ~ "No DBM"), # Usaremos esta
    DBM_2 = case_when(anemia == "Anemia" & peso_edad_dico == "Exceso de peso" ~ "DBM", TRUE ~ "No DBM"),
    DBM_3 = case_when(anemia == "Anemia" & peso_talla_dico == "Emaciacion" ~ "DBM", TRUE ~ "No DBM"),
    DBM_4 = case_when(anemia == "Anemia" & peso_talla_dico_1 == "Exceso de peso" ~ "DBM", TRUE ~ "No DBM")
  )

summary(dbm)

prop.table(table(dbm$peso_talla_dico))*100

prop.table(table(dbm$id1, dbm$DBM_4), margin = 1)*100

hist(dbm$talla_edad, breaks = 100, col = "lightblue", main = "Peso para la Edad", xlab = "Peso para la Edad")

ggplot(dbm, aes(x = as.factor(id1), fill = DBM_1)) + 
  geom_bar()

# Sin filtro
sin_pro <- ninios |>
  dplyr::mutate(
    talla_edad = hc70 / 100,
    anemia = case_when(hc57 == 4 ~ "Sin Anemia", TRUE ~ "Anemia"),
    talla_edad_dico = case_when(talla_edad < -2 ~ "DCI", TRUE ~ "Normal"),
    DBM_1 = case_when(anemia == "Anemia" & talla_edad_dico == "DCI" ~ "DBM", TRUE ~ "No DBM"))

test <- sin_pro |>
  dplyr::select(id1, DBM_1) |>
  dplyr::count(id1)

test

test_2 <- dbm |>
  dplyr::select(id1, DBM_1) |>
  dplyr::count(id1, DBM_1)

test_2
```

# Produce tables

## Table 1

```{r}
dbm |>
  dplyr::select(where(is.character), peso, -DBM_2, -DBM_3, -DBM_4) |>
  tidyr::pivot_longer(
    cols = c(anemia:peso_talla_dico_1),
    names_to = "Variable",
    values_to = "Valor"
  ) |>
  dplyr::group_by(Variable, Valor) |>
  dplyr::summarise(n = n(), weighted_prop = sum(peso)) |>
  dplyr::mutate(weighted_prop = round(weighted_prop / sum(weighted_prop) * 100, 2))
```

```{r}
tbl_svysummary <-
  survey::svydesign(
    ids = ~ 1,
    data = dbm,
    weights = ~ peso) |>
  tbl_svysummary(
    percent = "column",
    statistic = list(all_categorical() ~ "{n_unweighted} ({p})"),
    type   = all_categorical() ~ "categorical",
    digits = all_categorical() ~ c(0, 1)
  ) |>
  add_ci(
    method = list(all_categorical() ~ "svyprop.logit"),
    statistic = list(all_categorical() ~ "{conf.low} - {conf.high}"),
    style_fun = list(all_categorical() ~ purrr::partial(style_percent, digits = 1))
  ) |>
  bold_labels()

tbl_svysummary
```

## Table 2 (regression)

```{r}
design <- survey::svydesign(ids = ~ 1, data = dbm, weights = ~ peso)
```

```{r}
univ_tab <-
  tbl_uvregression(
    data = design,
    method = glm,
    method.args = list(quasipoisson(link = "log")),
    include = c(sexo:trabajo),
    y = FIES,
    hide_n = TRUE,
    exponentiate = TRUE,
    conf.int = TRUE,
    ci_method = "wald",
    tidy_fun = broom.helpers::tidy_parameters,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~style_pvalue(.x, digits = 3),
    estimate_fun = ~style_number(.x, digits = 2)) |>
  bold_labels() |>
  modify_footnote(everything() ~ NA, abbreviation = TRUE)
```

```{r}
table_3.1 <-
  glm(
    dx_nutricional ~ edad_del_nino.c + sexo + frecuencia_visita +
      lactancia_materna + edad_de_alimentacion_complementaria +
      presencia_de_alimentos_nutritivos + edad_materna.c + nivel_educativo +
      estado_civil + estado_civil + numero_de_miembros_en_el_hogar +
      ingreso_familiar + situacion_ocupacional + apoyo_familiar + toma_de_decisiones +
      comidas_al_dia_de_la_madre + mdd_w,
    data = data,
    family = quasipoisson(link = "log")) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)) |>
  bold_p(t = 0.05) |>
  add_vif() |>
  modify_footnote(update = everything() ~ NA, abbreviation = TRUE)
```

```{r}
data <- endes |>
  dplyr::select(urb_rur, region_natural, idx_riq, desague, agua, electricidad,
                combustible, agem_cat, primer_parto, num_child_cat, est_civ,
                lvl_educativo, sexo_jefe, agec_cat, sex_child, hierro_embarazo,
                weight_born_cat, tamano_percibido, actual_amamantando, 
                triple_burden, sample_weight_house)
colnames(endes)


data1 <- data |>
  dplyr::mutate(lactancia = case_when(actual_amamantando == 0 & agec_cat >= 2 ~ "P_>2years",
                                      actual_amamantando == 0 & agec_cat < 2 ~ "P_<2years",
                                      actual_amamantando == 1 & agec_cat >= 2 ~ "C_>2years",
                                      actual_amamantando == 1 & agec_cat < 2 ~ "C_<2years",
                                      FALSE ~ "Never"))

```
